### 2018-04-11 dissertation/4-project/chapter4.tex
prepare for final draft

In a network in which malicious nodes are a minority (under 50\%), it is expected that the benign nodes will form components with large numbers of nodes, because these benign nodes will share their networks with each other and it is easy to form trust paths between pairs of benign nodes.
Malicious nodes, on the other hand, do not send their own networks of false information to benign nodes, and might not always trust other malicious nodes, causing them to become isolated in small strongly connected components (in some cases, these contain a single malicious node).
The result is that most benign nodes become members of a small number of large components; when the component graph is colored, these components are likely to receive the same color, because two benign components are never adjacent.
Because of this, the coloring heuristic works as a classification method.
%Classifying the color that represents the most nodes as correct works because

@@

Then, when node $u$ interacts with another node $w$ in the future, $u$'s opinion of $v$ comes with the timestamp attached, so $w$ has the information to know how much time has passed since the interaction between $u$ and $v$ happened.
Once $w$ performs the graph merge procedure with $T_u$ and $T_w$, but $T_w$ already has an edge $u\rightarrow v$ stored, it checks the two timestamps and only updates the edge if the incoming information is more recent than what is already stored.
Since the timestamp is always set to the destination node of the edge, it can be used for comparison regardless of which nodes handled the information. 
Algorithm \autoref{algorithm:union_timestamp} shows how the union function was changed to accommodate timestamps and information aging.

@@

\subsection{Complexity}
The complexity of TruMan must calculated for each iteration executed and each node in the network.
It can be estimated by adding the complexity of most costly operations involved, which are: ($i$) Tarjan's algorithm, ($ii$) the graph coloring algorithm, and ($iii$) the graph union process.
Tarjan's algorithm and the graph coloring algorithm are executed once per iteration on each node of the network.
The graph union, however, is executed once every time a neighboring node shares information.
Each neighbor shares information once per iteration, so the complexity of the graph union procedure is multiplied by $n^u_i$, the number of neighbors node $u$ has during iteration $i$.

>>>>

In a network in which malicious nodes are a minority (under 50\%), it is expected that the benign nodes will form components with large numbers of nodes, because these benign nodes will share their networks with each other and it is easy to form trust paths between pairs of benign nodes.
Malicious nodes, on the other hand, do not send their own networks of false information to benign nodes, and might not always trust other malicious nodes, causing them to become isolated in small strongly connected components (in some cases, these contain a single malicious node).
The result is that most benign nodes become members of a small number of large components; when the component graph is colored, these components are likely to receive the same color, because two benign components are never adjacent.
Because of this, the coloring heuristic works as a classification method.
A high scale collusion attack could affect this heuristic, as malicious nodes would form large components and distinguishing these components from the benign ones would be a challenge.
%Classifying the color that represents the most nodes as correct works because

@@

Then, when node $u$ interacts with another node $w$ in the future, $u$'s opinion of $v$ comes with the timestamp attached, so $w$ has the information to know how much time has passed since the interaction between $u$ and $v$ happened.
Once $w$ performs the graph merge procedure with $T_u$ and $T_w$, but $T_w$ already has an edge $u\rightarrow v$ stored, it checks the two timestamps and only updates the edge if the incoming information is more recent than the node already had stored.
Since the timestamp is always set to the destination node of the edge, it can be used for comparison regardless of which nodes handled the information. 
Algorithm \autoref{algorithm:union_timestamp} shows how the union function was changed to accommodate timestamps and information aging.

@@

\subsection{Complexity}
The complexity of TruMan must be calculated for each iteration executed and each node in the network.
It can be estimated by adding the complexity of most costly operations involved, which are: ($i$) Tarjan's algorithm, ($ii$) the graph coloring algorithm, and ($iii$) the graph union process.
Tarjan's algorithm and the graph coloring algorithm are executed once per iteration on each node of the network.
The graph union, however, is executed once every time a neighboring node shares information.
Each neighbor shares information once per iteration, so the complexity of the graph union procedure is multiplied by $n^u_i$, the number of neighbors node $u$ has during iteration $i$.

### 2018-04-11 dissertation/5-simulations/chapter5.tex
prepare for final draft

The choice of the Working Day Movement Model for evaluations is more strongly related to inter-contact times.
For reasons explained in \autoref{chapter:truman}, relatively short inter-contact times is important for TruMan's functionality.
Contact duration time is an important metric to measure how much data can be exchanged during each encounter, although, for this evaluation, it was not considered.

@@

$$ \delta = \frac{\frac{30^2\pi}{2} \times 160}{14.689.750} = 0.0154$$

@@

@@

\caption{Simulation with $\rho$ = 10m and varying percentages of malicious nodes (1/2).}
\label{fig:randommalicious1}
\end{figure}

\caption{Simulation with $\rho$ = 10m and varying percentages of malicious nodes (2/2).}
\label{fig:randommalicious2}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{images/plots/Network_rA7/10_10}
\caption{7 days scenario: 10m range and 10\% malicious nodes.} \label{fig:random7}
\end{figure}

\caption{Simulation with information aging, with different maximum age values (1/2).}
\label{fig:extramaliciousaging1}
\end{figure}

\caption{Simulation with information aging, with different maximum age values (2/2).}
\label{fig:extramaliciousaging2}
\end{figure}

>>>>

The choice of the Working Day Movement Model for evaluations is more strongly related to inter-contact times.
For reasons explained in \autoref{chap:truman}, relatively short inter-contact times is important for TruMan's functionality.
Contact duration time is an important metric to measure how much data can be exchanged during each encounter, although, for this evaluation, it was not considered.

@@

$$ \delta = \frac{\frac{30^2\pi}{2} \times 160}{14,689,750} = 0.0154$$

@@

\caption{Simulation with $\rho$ = 10m and varying percentages of malicious nodes (1\%, 5\% and 10\%).}
\label{fig:randommalicious1}
\end{figure}

\caption{Simulation with $\rho$ = 10m and varying percentages of malicious nodes (30\%, 40\% and 50\%).}
\label{fig:randommalicious2}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{images/plots/Network_rA7/10_10}
\caption{7 days scenario: 10m range and 10\% malicious nodes.} \label{fig:random7}
\end{figure}

\caption{Simulation with information aging, with different maximum age values ($m=10, 250$).}
\label{fig:extramaliciousaging1}
\end{figure}

\caption{Simulation with information aging, with different maximum age values ($m=1000, 5000$).}
\label{fig:extramaliciousaging2}
\end{figure}

@@
